TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-10 paper.tex
future work

\section{Future Work} -Amanda
Duplicating channels (a little renaming or sharing arrays with mutexes)\\
Optimizations to reduce overhead\\

>>>>

\section{Future Work}
Future work is focused on saving memory by using channel and code reuse optimizations when forking new chain programs from current tasks. 
When forking a new task, a channel may be duplicated, which linearly increases the amount of memory neceesary for channels with the number of currently running programs.
It is possible to reuse channels between tasks if the number of iterations of that task are known at compile time and it can be estimated how 
many are to be running simulateously. A register allocation graph coloring scheme can then be repurposed for reusing channels allocated at compile time.
In either case the current channel naming scheme must be changed to support channel duplication, ether real or simulated.
Currently channels are allocated and named at compile time by combining the names of the input and output channel tasks. 
However, if tasks can be duplicated this naming scheme must be altered to support multiple channels of the same name and potentially multiple channels of the same name.
This can be done with a vector clock timestamp or a simple counter stored in nonvolatile memory to create unique channel names.\\

Additionally, it is possible to save memory by sharing arrays between tasks without the necessity of copying the array in its entirety in each channel.
To do this the concept of interrmittent tasks mutexes for shared resources and data structures would be introduced.
The structures are protected by a lock that contains the thread ID of the task that currently holds the lock.
In order to allow all tasks access to a data structure without breaking all chain semantics, a modified version of a module channel would be used in order 
for multiple tasks to potentially modify one channel. 
However, even with that change it is challenging to define sharing between threads in an intermittent context and to maintain chain semantics while implementing 
shared data structures while still maintaining correctness. 
Because channel sizes are constrained at compile time currently, it is also necessary to know at compile time all data structures, shared or private, 
that are going to be used during execution of a chain program or programs. 
It is a challenge for future work in this field to constrain memory for channels at compile time and for the compiler to know with certainty how much memory 
is necessary to allocate. Depending on the workload, the amount of forked threads would need to be constrained such that threads don't overflow nonvolatile memory at runtime.\\

Future work also includes optimizations to reduce overhead, such as converting the free indices array to a free indices bitmap in order to reduce the amount of 
baseline memory that the scheduler task uses. 
Re-assignation and re-use of channels at runtime would increaes overhead, but it is thought that the memory saved by this procedure is worth the trade-off of increased overhead. If re-assignation can be determined at compile-time, the overhead during runtime will still remain low.\\
